---
title: "encharter"
output: github_document
---

<!-- badges: start -->
[![R-CMD-check.yaml](https://github.com/JanMarvin/encharter/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/JanMarvin/openxlsx2/actions/workflows/check-standard.yaml)
[![codecov](https://codecov.io/gh/JanMarvin/encharter/graph/badge.svg?token=JMMBBBHPTG)](https://codecov.io/gh/JanMarvin/encharter)
<!-- badges: end -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Experimental package that is still in early development.

This is a lightweight R6-based engine for generating Office Open XML (OOXML) charts. It is designed for users who need precise control over chart internals—such as combining multiple chart types, mapping secondary axes, or handles numeric XY coordinates in scatter and bubble plots—without the overhead of a full spreadsheet suite.

```{r}
library(openxlsx2)
library(encharter)

# 1. Create workbook and dummy data
wb <- wb_add_worksheet(wb_workbook(), sheet = "Data")
df_combo <- data.frame(
  Month = month.abb,
  Revenue = c(200, 220, 210, 250, 280, 300, 320, 310, 340, 360, 380, 400),
  Growth = c(0, 0.1, -0.04, 0.19, 0.12, 0.07, 0.06, -0.03, 0.1, 0.06, 0.05, 0.05)
)
wb <- wb_add_data(wb, sheet = "Data", x = df_combo)

# 2. Initialize and configure the Chart
combo_chart <- Chart$new()
combo_chart$set_chart_title("Monthly Revenue & Growth")

# Primary Axis: Revenue Bars
combo_chart$add_series(
  header = "Data!$B$1",
  cat    = "Data!$A$2:$A$13",
  data   = "Data!$B$2:$B$13",
  color  = "4472C4",
  type   = "barChart"
)

# Secondary Axis: Growth Line
combo_chart$add_series(
  header    = "Data!$C$1",
  cat       = "Data!$A$2:$A$13",
  data      = "Data!$C$2:$C$13",
  type      = "lineChart",
  secondary = TRUE,
  color     = "ED7D31",
  marker    = "circle"
)

wb <- wb_add_chart(wb, sheet = "Data", chart_obj = combo_chart)
```

```{r}
# 1. Create dummy waterfall data
df_wf <- data.frame(
  Label = c("Gross Revenue", "COGS", "OpEx", "Tax", "Net Income"),
  Value = c(1000, -400, -200, -100, 300)
)
wb <- wb_add_worksheet(wb, sheet = "WaterfallData")
wb <- wb_add_data(wb, sheet = "WaterfallData", x = df_wf)

# 2. Initialize and configure the Waterfall Chart
wf_chart <- ChartEx$new()
wf_chart$set_chart_title("Net Income Bridge")

wf_chart$add_series(
  header = "",
  cat    = "WaterfallData!$A$2:$A$6",
  data   = "WaterfallData!$B$2:$B$6"
)

wb <- wb_add_chartx(wb, chart_obj = wf_chart)
```

```{r}
# 1. Create dummy scatter data
df_scatter <- data.frame(
  Project = paste("Project", LETTERS[1:5]),
  Risk    = c(10, 40, 30, 70, 90),
  ROI     = c(20, 50, 80, 40, 60)
)
wb <- wb_add_worksheet(wb, sheet = "ScatterData")
wb <- wb_add_data(wb, sheet = "ScatterData", x = df_scatter)

# 2. Initialize and configure Scatter Chart
sc_chart <- Chart$new("scatterChart")
sc_chart$set_chart_title("Risk vs ROI Analysis")

sc_chart$add_series(
  header    = "Portfolio",
  cat       = "ScatterData!$B$2:$B$6", # X-axis (Risk)
  data      = "ScatterData!$C$2:$C$6", # Y-axis (ROI)
  show_line = FALSE,
  marker    = "circle",
  marker_size = 8
)

wb <- wb_add_chart(wb, sheet = "ScatterData", chart_obj = sc_chart)
```

